---
title: "README"
author: "Thomas Pin"
date: "17/02/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(tidyverse)
```

```{r readfile, include=FALSE}

mst3k_movies <- read_csv("table/mst3k_movies.csv", col_names = c("Index", "Movie", "Year", "IMDb Rating"), skip = 1)

negative_words <- read_csv("table/negative_words.csv", col_names = c("Index", "Word", "Weight"), skip = 1)

negative_ngrams2 <- read_csv("table/negative_ngrams2.csv", col_names = c("Index", "Word", "Weight"), skip = 1)

negative_words <- negative_words %>% 
  select(-Index)

mst3k_movies <- mst3k_movies %>% 
  select(-Index)

negative_ngrams2 <- negative_ngrams2 %>% 
  select(-Index)

```

# Artical Links 


## Words that relate to negative reviews 

The following is a list of words that are strongly correlated with negative movie reviews on IMDb 

```{r negative words}
kable(negative_words)
```

## MST3K movies 

The following movies were mentioned in reviews that contained MST3K. 

```{r mst3k}
kable(mst3k_movies)
```

## N-grams words that relate to negative reviews

The following is a list of words that are strongly correlated with negative movie reviews on IMDb

```{r ngrams2}
kable(negative_ngrams2)
```